Endogenous Heterogeneous Innovation

### 2018-03-07 Presentations/Proposal/SE-Presentation.tex
The first draft of the presentation slides along with some new code.

\documentclass[11pt]{beamer}
\usetheme{CambridgeUS}
\usecolortheme{lily}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{outlines}
\usepackage{graphicx}
\usepackage{xcolor}
\newcommand{\indep}{\rotatebox[origin=c]{90}{$\models$}}
\usepackage[numbers]{natbib}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{dcolumn}
\captionsetup{skip=0.333\baselineskip}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\newcommand\mc[1]{\multicolumn{1}{@{}c@{}}{#1}} % handy shortcut macro
\bibliographystyle{acm}
\author{Julio B. Roll \\ Scott Behmer}
\title{Heterogeneous Innovation and Intertemporal Productivity Choice}
%\subtitle{}
\setbeamercovered{transparent} 
\definecolor{brightmaroon}{rgb}{0.76, 0.13, 0.28}
\setbeamercolor{frametitle}{fg=brightmaroon}
\setbeamercolor{title}{fg=brightmaroon}
\setbeamertemplate{navigation symbols}{} 
%\logo{} 
%\institute{} 
\date{February 14, 2018} 
%\subject{}

@@

\begin{frame}{Research Motivation}
	Since the rebirth of endogenous growth in mid-2000s, literature became richer:
	\begin{itemize}\itemsep12pt
	\item Classics: Romer (1990), Grossman and Helpman (1991), Aghion and Howitt (1992);
	\item Micro-data renewal: Klette and Kortum (2004), Lentz and Mortensen (2008);
	\item Current state of the art: Acemoglu et al. (2013), Akcigit and Kerr (2016).
	\end{itemize}
$\Rightarrow$ We now account for creative destruction/turnover, R\&D spillover, imitation, incumbents' innovation, firm heterogeneity...but...
\end{frame}

%being generous: riskless rate not added, only sales - cogs, other expenses lacking

\begin{frame}{Research Motivation}
	\begin{center}
	\begin{figure}\centering\label{Ratio_firms}
	  \fbox{\resizebox{3.8in}{2.6in}{\includegraphics{Ratio_firms.jpeg}}}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}{Research Motivation}
	\begin{center}
	\begin{figure}\centering\label{Ratio_emp}
	  \fbox{\resizebox{3.8in}{2.6in}{\includegraphics{Ratio_emp.jpeg}}}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}{Research Motivation}
	\textbf{Questions:}
	\begin{itemize}\itemsep12pt
		\item What's the impact of intertemporal TFP choice on aggregate TFP?
		% (short-term, long-term)
		\item What are the implications to the innovation strategy of firms? 
		\item How long does it take to "get TFP back"?
		%time span of intertemporal change cycle
	\end{itemize}	 
	\textbf{Why is it interesting?}
    \begin{itemize}\itemsep12pt
	\item Having Bluetooth in your car $\neq$ Tesla, or innovation heterogeneity sparks different firm behavior;
	%especially abrupt innovation
	\item Less TFP now for more TFP latter could impact aggregate measurement;
	\item Finance has a role in "footing the bill" and reallocation;
	\item Normative: how to spur abrupt innovation?
	\end{itemize}
\end{frame}

%"say I'm Toyota...", product life-cycle

\begin{frame}{Framework - Innovation}
	\textbf{Focus:} Innovation: internal (incremental or abrupt), external, and entrants (the last two only abrupt).
	%my contribution (internal innovation = higher markups)
	\begin{center}
	\begin{figure}\centering\label{Innov2}
	  \fbox{\resizebox{3.2in}{2.2in}{\includegraphics{Innov_2.png}}}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}{Framework - Innovation}
	\textbf{Focus:} Innovation: internal (incremental or abrupt), external, and entrants (the last two only abrupt).
	%my contribution (internal innovation = higher markups)
	\begin{center}
	\begin{figure}\centering\label{Innov3}
	  \fbox{\resizebox{3.2in}{2.2in}{\includegraphics{Innov_3.png}}}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}{Framework - Innovation}
	\textbf{Focus:} Innovation: internal (incremental or abrupt), external, and entrants (the last two only abrupt).
	%my contribution (internal innovation = higher markups)
	\begin{center}
	\begin{figure}\centering\label{Innov4}
	  \fbox{\resizebox{3.2in}{2.2in}{\includegraphics{Innov_4.png}}}
	\end{figure}
	\end{center}
\end{frame}

@@

\begin{frame}{Framework - Innovation}
	\textbf{Focus:} Innovation: internal (incremental or abrupt), external, and entrants (the last two only abrupt).
	%my contribution (internal innovation = higher markups)
	\begin{center}
	\begin{figure}\centering\label{Innov6}
	  \fbox{\resizebox{3.2in}{2.2in}{\includegraphics{Innov_6.png}}}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}{Framework - Innovation}
	\textbf{Focus:} Innovation: internal (incremental or abrupt), external, and entrants (the last two only abrupt).
	%my contribution (internal innovation = higher markups)
	\begin{center}
	\begin{figure}\centering\label{Innov7}
	  \fbox{\resizebox{3.2in}{2.2in}{\includegraphics{Innov_7.png}}}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}{Framework - Innovation}
	\begin{itemize}\itemsep10pt	
	\item Law of motion ($A_{m+1} = A_m\gamma_{int, pot}$): $A_{t+\Delta t} =\begin{cases}
               A_m(1-\alpha^{s})\:,\: \lambda_{inc}\Delta t \:,\: \alpha \in (0,1)\:,\:\ s \in \{1, 2, ...\}\\
               A_t\gamma_{int,abr}\:,\: \lambda_{int,abr}\Delta t\\
               A_t \:, \: \big[1 - \lambda_{inc}\Delta t; 1 - \lambda_{int,abr}\Delta t\big] 
    \end{cases}$
	\item Incremental R\&D cost: $\psi_{inc}(\lambda_{inc}, A_{t}) = \xi_j A_t \lambda_{inc}^{\eta}$
	\item Catching-up: laggards pay $\psi_{inc}(\lambda_{inc}, A_{t})$ and get an arrival $\lambda_{inc} + h$;
	\item Abrupt R\&D cost (for $n_p > 0$): $\psi_{abr}(\lambda_{ext,abr}, \bar{A}_{t}) = \xi_j \bar{A}_t \lambda_{ext,abr}^{\eta}\:$, $\bar{A}_{t}$ sector average;
	%average, to eliminate dependence on R&D level (cst fraction of total expenditure), levels out with returns
	\item Cournot competition: profits $\pi_t$ scale with $\frac{A_{j,i,m}}{\sum_{j}A_{j,i,m}}$ within an industry.
	\end{itemize}
\end{frame}

\begin{frame}{Empirical Work - Patents}
How to discipline $\{\alpha, \gamma_{int, abr}, \gamma_{ext,abr},\gamma_{int, pot}\}$?
	\begin{itemize}\itemsep12pt	
		\item USPTO patent data (e.g. \# patents, \# patent citations, if it's self-citation or external...).
		%data linked to Compustat
	\end{itemize}
Model (complete):
	\begin{itemize}
		\item Endogenous: R\&D, productivity (all parameters);
		\item Exogenous: labor market (wages, supply), consumers (discounting), mass of entrants;
		\item Estimated (for Patents): $\{\alpha, \gamma_{int, abr}, \gamma_{ext,abr},\gamma_{int, pot}\}$;
		\item Calibrated (for Complete version): discounting, curvature of the R\&D cost function ($\eta$).
	\end{itemize}
\end{frame}

\begin{frame}{Empirical Work - Patents}
	\begin{center}
	\begin{figure}\centering\label{Innov7}
	\begin{minipage}[b]{0.45\linewidth}
	  \fbox{\resizebox{2.0in}{1.8in}{\includegraphics{Patent_citation_distr.png}}}
	\end{minipage}
	\begin{minipage}[b]{0.45\linewidth}
		\fbox{\resizebox{2.0in}{1.8in}{\includegraphics{Patent_citation_distr_cut.png}}}
	\end{minipage}
	\end{figure}
	\end{center}
	Summary: \# obs = 3,278,174; Mean = 11.76; Std. Dev. = 20.00
\end{frame}

\begin{frame}{Empirical Work - Patents}
GMM strategy:
	\begin{itemize}\itemsep12pt	
		\item Each patent in the data set can be classified as internal or external (based on whether the company has previous patents within that classification) and incremental versus abrupt (based on the number of citations that the patent has);
		\item Given a guess of parameter values $\{\alpha, \gamma_{int, abr}, \gamma_{ext,abr},\gamma_{int, pot}\}$, we can calculate the moments;
		\item Potential moments to use: average rate of internal, abrupt patents; average rate of external, abrupt patents; average rate of internal, incremental patents; correlation between abrupt and incremental patent rates.
		%ideally: product cycle data
	\end{itemize}
\end{frame}

\begin{frame}{Conclusion}
\begin{itemize}\itemsep12pt	
		\item Goal: estimate the R\&D part of an endogenous growth model with heterogeneous innovation;
		\item Possibilities: 
		\begin{itemize}\itemsep12pt
			\item Add firm-level financials and estimate the parameters of the Partial Equilibrium (indirect inference);
			\item Solve the SS;
			\item Cure cancer...
		\end{itemize}
		\item Caveats: lots of firms don't innovate, patents do not represent innovation (nor products, ideally we would have product-level data).
	\end{itemize}
\end{frame}

@@

>>>>

\documentclass[11pt]{beamer}
\usetheme{CambridgeUS}
\usecolortheme{lily}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{outlines}
\usepackage{graphicx}
\usepackage{xcolor}
\newcommand{\indep}{\rotatebox[origin=c]{90}{$\models$}}
\usepackage[numbers]{natbib}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{dcolumn}
\captionsetup{skip=0.333\baselineskip}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\newcommand\mc[1]{\multicolumn{1}{@{}c@{}}{#1}} % handy shortcut macro
\bibliographystyle{acm}
\author{Julio B. Roll \\ Scott Behmer}
\title{Endogenous Heterogeneous Innovation}
%\subtitle{}
\setbeamercovered{transparent} 
\definecolor{brightmaroon}{rgb}{0.76, 0.13, 0.28}
\setbeamercolor{frametitle}{fg=brightmaroon}
\setbeamercolor{title}{fg=brightmaroon}
\setbeamertemplate{navigation symbols}{} 
%\logo{} 
%\institute{} 
\date{February 14, 2018} 
%\subject{}

@@

\begin{frame}{Theory Outline}
	\begin{itemize}\itemsep12pt
	\item Akcigit and Kerr (2016) included two different types of innovation (incremental and abrupt). Firms had no control over what type of innovation their R\&D efforts would result in.
	\item Julio (2018 working paper) endogenizes this distinction. Firms choose how much to invest in abrupt or internal innovations.
	\item We attempt to fit this model to patent citation distributions. The fit gives an impression of how well the model reflects reality. Also, the resulting parameter values have important theoretical interpretations.
	\end{itemize}
\end{frame}

@@

%The graphics in this slide need to be updated. I want it to have the histogram of abrupt patent citations that we are fitting the model to.
\begin{frame}{Data - Patent Citation Distributions}
	\begin{center}
	\begin{figure}\centering\label{Innov7}
	\begin{minipage}[b]{0.45\linewidth}
	  \fbox{\resizebox{2.0in}{1.8in}{\includegraphics{Patent_citation_distr.png}}}
	\end{minipage}
	\begin{minipage}[b]{0.45\linewidth}
		\fbox{\resizebox{2.0in}{1.8in}{\includegraphics{Patent_citation_distr_cut.png}}}
	\end{minipage}
	\end{figure}
	\end{center}
	Summary: \# obs = 3,278,174; Mean = 11.76; Std. Dev. = 20.00
\end{frame}

\begin{frame}{Theoretical Assumptions Regarding Patent Citations}
	\begin{itemize}\itemsep12pt	
		\item An abrupt patent is cited by every subsequent innovation within its technology cluster.
		\item Technology clusters are all contained within a patent classification.
		\item Abrupt patents will have a large number of citations overall (within and outside of their patent classifications)
		\item We need to choose a cutoff for distinguishing abrupt patents. The default is ten percent. Later we test the robustness of our estimates to changes in this cutoff.
	\end{itemize}
\end{frame}

\begin{frame} {Parameters}
	\begin{itemize}\itemsep 12pt
		\item Three parameters to estimate $\{\alpha , \lambda_{int, 0}, \lambda_{abr} + \tau \}$
		\item $\alpha$ relates to the diminishing returns of incremental innovations. A low $\alpha$ means that the step-size decreases very quickly. $\alpha = 1$ means that step sizes are constant.
		\item $\lambda_{int, 0}$ is the rate of incremental innovations for new technology clusters. It is actually a function of the exogenous parameters $\{D, \sigma, \psi\}$, which cannot be separated using citation distributions.
%Julio needs to update these other parameters
		\item $\lambda_{abr} + \tau$ is the total arrival rate of abrupt innovations. It is also a function of exogenous parameters.
	\end{itemize}
\end{frame}

\begin{frame} {Estimation Strategy}
	\begin{itemize}\itemsep 12pt
		\item First the parameters $\{alpha,\lambda_{int, 0}/ (\lambda_{abr} + \tau) \}$ are estimated using MLE on the abrupt, same-class citation distribution.
		\item Next the absolute values of $\lambda_{int, 0}$ and $\lambda_{abr} + \tau$ are determined using compustat data on R\&D intensity.
	\end{itemize}
\end{frame}

\begin{frame} {Estimation Results}
	\begin{itemize}\itemsep 12pt
		\item $\alpha = 1$, $\lambda_{int, 0}= 0.357 $, $(\lambda_{abr} + \tau = 0.355 $
		\item Insert histogram with MLE curve on it. Comment on how the alpha estimate implies constant step size. Talk about missing the mass at zero citations.
	\end{itemize}
\end{frame}

\begin{frame} {Confidence in global optimum}
	\begin{itemize}\itemsep 12pt
		\item The result is robust to changes in initial conditions.
		\item We tried fixing $\alpha$ and running an unconstrained optimization. This gave the same results.
		\item Show or discuss the 3d plot of the likelihood function.
	\end{itemize}
\end{frame}

\begin{frame} {Robustness}
	\begin{itemize}\itemsep 12pt
		\item GMM results: 
		\item When the cutoff for abrupt patents is adjusted, we get similar results (insert table of results).
		\item Relax the assumption that abrupt patents are cited by every incremental patent in their technology cluster, insert results.
		\item Importantly, across all robustness checks, $\alpha$ is always found to be equal to one.
		\item Still, there are doubts about other theoretical assumptions.
	\end{itemize}
\end{frame}

\begin{frame}{Conclusion}
\begin{itemize}\itemsep12pt	
		\item The model fits most of the citation distribution, but badly underestimates the number of  patents with zero citations.
		\item No evidence was found for an important feature of the model: the diminishing return from incremental innovations.
		\item We are confident, given our theoretical specification, that we have found the parameters that maximize the log-likelihood.
		\item Our results pass a number of robustness checks.
		\item However, many key theoretical assumptions are still unchecked.
	\end{itemize}
\end{frame}

@@

\begin{frame}{Appendix: Framework - Innovation}
	\begin{itemize}\itemsep10pt	
	\item Law of motion ($A_{m+1} = A_m\gamma_{int, pot}$): $A_{t+\Delta t} =\begin{cases}
               A_m(1-\alpha^{s})\:,\: \lambda_{inc}\Delta t \:,\: \alpha \in (0,1)\:,\:\ s \in \{1, 2, ...\}\\
               A_t\gamma_{int,abr}\:,\: \lambda_{int,abr}\Delta t\\
               A_t \:, \: \big[1 - \lambda_{inc}\Delta t; 1 - \lambda_{int,abr}\Delta t\big] 
    \end{cases}$
	\item Incremental R\&D cost: $\psi_{inc}(\lambda_{inc}, A_{t}) = \xi_j A_t \lambda_{inc}^{\eta}$
	\item Catching-up: laggards pay $\psi_{inc}(\lambda_{inc}, A_{t})$ and get an arrival $\lambda_{inc} + h$;
	\item Abrupt R\&D cost (for $n_p > 0$): $\psi_{abr}(\lambda_{ext,abr}, \bar{A}_{t}) = \xi_j \bar{A}_t \lambda_{ext,abr}^{\eta}\:$, $\bar{A}_{t}$ sector average;
	%average, to eliminate dependence on R&D level (cst fraction of total expenditure), levels out with returns
	\item Cournot competition: profits $\pi_t$ scale with $\frac{A_{j,i,m}}{\sum_{j}A_{j,i,m}}$ within an industry.
	\end{itemize}
\end{frame}
